Sex and Power: Sexual dimorphism in trait variability and its eco-evolutionary

### 2020-09-09 scripts/MouseSexDiffVar_05_2020.Rmd
Still not sure why rendering is failing. Seems to be some issue with gather. Works fine when I run on it's own, but ony when knitting does it fail

---
title: 'Sex and Power: Sexual dimorphism in trait variability and its eco-evolutionary
  and statistical implications'
author: Susanne Zajitschek,  Felix Zajitschek, Russell Bonduriansky, Robert  Brooks,
  Will Cornwell, Daniel Falster, Malgorzata Lagisz, Jeremy Mason, Alistair Senior,
  Daniel Noble, & Shinichi Nakagawa
date: "`r Sys.Date()`"
output:
  bookdown::html_document2:
    code_folding: hide
    number_sections: yes
    theme: flatly
    toc: yes
    toc_depth: 6
    toc_float: yes
  bookdown::pdf_document2:
    toc: yes
    toc_depth: 6
    number_sections: true
    theme: flatly
  word_document:
    toc: yes
    toc_depth: '4'
  html_notebook:
    toc: yes
  html_document:
    df_print: paged
    toc: yes
    toc_depth: '4'
  bookdown::word_document2:
    toc: yes
    toc_depth: 6
    number_sections: true
    theme: flatly
subtitle: Electronic Supplementary Material
always_allow_html: yes
---

>>>>

---
title: 'Sex and Power: Sexual dimorphism in trait variability and its eco-evolutionary
  and statistical implications'
author: Susanne Zajitschek,  Felix Zajitschek, Russell Bonduriansky, Robert  Brooks,
  Will Cornwell, Daniel Falster, Malgorzata Lagisz, Jeremy Mason, Alistair Senior,
  Daniel Noble, & Shinichi Nakagawa
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
    toc: yes
    toc_depth: '4'
  bookdown::pdf_document2:
    toc: yes
    toc_depth: 6
    number_sections: true
    theme: flatly
  word_document:
    toc: yes
    toc_depth: '4'
  html_notebook:
    toc: yes
  bookdown::html_document2:
    code_folding: hide
    number_sections: yes
    theme: flatly
    toc: yes
    toc_depth: 6
    toc_float: yes
  bookdown::word_document2:
    toc: yes
    toc_depth: 6
    number_sections: true
    theme: flatly
subtitle: Electronic Supplementary Material
always_allow_html: yes
---
